\documentclass[a4paper,11pt,oneside]{article}
\usepackage[left=2.5cm,right=2.0cm,top=2cm,bottom=2.0cm]{geometry}
\usepackage{HS,lipsum}
\usepackage{graphicx}
\usepackage{lastpage}

\begin{document}
\begin{mcdletter}[Material Request: Fan Coil Units]


Please obtain quotations and process the necessary documentation for the above materials, as early as possible and provide us with your recommendations and price comparisons in order for us to release the order. 

We attach the following documentation for the enquiry. 

\begin{enumerate}

\item Specification (Incorporated in Compliance Statement)
\item Full Mechanical and Electrical Specification
\item List of Suppliers
\item Compliance Statement
\end{enumerate}

Please note that the following must be included with the Suppliers offers:

\begin{enumerate}
\item Units to be selected at medium speed. Supplier to quote the amount saved if units are selected at high speed.
\item  Operations and Maintenance manuals to be delivered at the same time as the Equipment or earlier and to comply with the Contract Requirements in terms of formats and approvals (i.e., they need to be submitted for approval before shipping of the units).
\item Spare Parts as per specification to be quoted and a separate price as per manufacturer's recommendations.
\item Warranty of 400 days from Handover to Owner.
\item Commissioning of Equipment.
\end{enumerate}

Please also note that external static calculations are at this stage, as per Engineer's estimates. Final values will be provided before proceeding with order/delivery, as well as specify left and right units.


Please ensure that all Suppliers complete the Compliance statement and that these are sent to us together with all the relevant details for our evaluation and approval. Preference will be given to Suppliers providing full information/submittals at the quotation stage. Any Supplier not completing the Compliance Statement will summarily be excluded from our evaluation.



\end{mcdletter}

\end{document}