\documentclass[a4paper,12pt,oneside]{article}
\usepackage[left=2.5cm,right=2.0cm,top=2cm,bottom=2.0cm]{geometry}
\usepackage{HS}
\usepackage{hyperref}


\begin{document}


\begin{mcdletter}[Subcontract Release Note: Fire Alarm and Voice Evacuation]

We attach the following documentation for the enquiry.

\begin{enumerate}    
\item Full Mechanical and Electrical specifications to which the Subcontractor will need to comply fully.
\item All related drawings
\item List of Suppliers.
\item Compliance Statement.
\end{enumerate}

Please note that the following must be included fully with the Supplier's offer.

\begin{enumerate}
\item Supply and installation of all equipment and detail design and Engineering of all services related to the Fire Alarm and Voice Evacuation System.

\item Subcontractor to allocate full-time staff on-site for the preparation of drawings and submittals as required by the Contract. During installation subcontractor is expected to installl all the equiment provided in its Contract and carry out all wiring and terminations. HLS will provide only power to the subcontractor's equipment and terminate.  All containment will be provided by the HLS/DS JV.

\item Operations and Maintenance Manuals to be delivered at the same time as the Equipment or earlier and to comply with the Contract Requirements in terms of formats and approvals.

\item Spare Parts as per specification to be quoted and a separate price as per manufacturer's recommendations.

\item Warranty as per Contract Conditions of 400 days from Handover to Owner.

\item Commissioning of equipment including progressive commissioning as systems are completed.
\end{enumerate}

Please ensure that all Suppliers complete the Compliance Statement and that these are sent to us together with all relevant details for our evaluation and approval. Preference will be given to Suppliers providing full information/submittals at the quotation stage. Any Supplier not completing the Compliance Statement will summarily be excluded from our evaluation.
\end{mcdletter}
\end{document}