\documentclass[a4paper,12pt,oneside]{article}
\usepackage[left=2.5cm,right=2.0cm,top=2cm,bottom=2.0cm]{geometry}
\usepackage{HS}


\begin{document}


\begin{mcdletter}[Subcontract Release Note: GI Ducts]

We attach the following documentation for the enquiry.

\begin{enumerate}    
\item Mechanical specification.
\item All related drawings
\item List of Suppliers.
\item Compliance Statement.
\end{enumerate}

Please note that the following must be confirmed  with the Supplier's offer.

\begin{enumerate}
\item Supply and delivery to Site of ductwork within 7 days from the release of Site Requisition and sketches. Ductwork will be released as per Site progress and is estimated that will be in excess of 300 tonnes in total.

\item Subcontractor to supply ductwork and accessories fully tagged as per approved and agreed tagging system and in full runs, as per requisition.

\item All ductwork to be provided with sealant applied at the factory.

\item All ductwork will go through Site QA/QC ductwork not approved by the Engineer will have to be removed from site and replaced within 3 days at no cost.

\item Method of calculating square meters of ducting to be provided with offer. (Must conform with acceptable International QS Standards).

\item Factory must have ISO certification.

\item Prices to be fixed for the duration of the contract.

\end{enumerate}

Please ensure that all Suppliers complete the Compliance Statement and that these are sent to us together with all relevant details for our evaluation and approval. Preference will be given to Suppliers providing full information/submittals at the quotation stage. Any Supplier not completing the Compliance Statement will summarily be excluded from our evaluation.

Please note to safe-guard deliveries we will split the orders to  two Suppliers.
\end{mcdletter}
\end{document}