\documentclass[a4paper,11pt,oneside]{article}
\usepackage[left=2.5cm,right=2.0cm,top=2cm,bottom=2.0cm]{geometry}
\usepackage{HS,lipsum}
\usepackage{graphicx}
\usepackage{lastpage}


\begin{document}


\begin{mcdletter}[Subcontract: Prefabrication Corridor MEP]


Please obtain quotations and process the necessary documentation for the above subcontract, as early as possible and provide us with your recommendations and price comparisons in order for us to release the order. As this is on the Project Critical Path, we would appreciate if pricing can be concluded within 30 days from the receipt of this letter.

We attach the following documentation for the enquiry. 

\begin{enumerate}

\item Specification (Incorporated in Compliance Statement)
\item Full Mechanical and Electrical Specification
\item List of Suppliers
\item Drawings
\end{enumerate}

\subsection*{Scope of works}

The scope of works include the turnkey design, prefabrication delivery to Site and Installation of the following:

\begin{enumerate}
\item  Ductwork including insulation and all accessories
\item  Fire protection. 
\item  Fire Detection (Containment).
\item  BMS containment.
\item  ELV services containment.
\item  All other services as shown on the drawings.
\item  Electrical power cables.
\item  H\&C water services where applicable.
\end{enumerate}



Please ensure that all Suppliers complete the Compliance statement and that these are sent to us together with all the relevant details for our evaluation and approval. Preference will be given to Suppliers providing full information/submittals at the quotation stage. Any Supplier not completing the Compliance Statement will summarily be excluded from our evaluation.



\end{mcdletter}

\end{document}